Happiness versus Income Awareness

### 2022-02-28 outputs/paper/Paper2-copy.Rmd
final before

---
title: "Happiness versus Income Awareness"
subtitle: "Will people be happier if they know each other's income?"
author: 
  - Xiao Bai
  - Yichun Zhang
date: "20/02/2022"
output:
  pdf_document:
    toc: true
    toc_depth: 2
abstract: "In 2001, tax records in Norwey becaome easily accessible online, which allows everyone to see their income level and make comparsion with other people's income. The populatiry of searching the word "Skattelister" (tax record list) has increased significantly since the introduction of tax data in 2001. People has large interest in the tax lists: for every five searches for YouTube, there was about one for skattelister. However, the introduction of this tax record list would cause a negative effect on the public as the income comparision model reports that the visible income transparency can exntend the disparity in well-being between groups of people with higher and lower income. "
bibliography: references.bib
---

@@

Based on information gathered by the Norwegian Monitor Survey, an annual self-completion questionnaire was disseminated to an ethnically diverse sample of Norwegians between 1985 and 2013. In terms of several apparent qualities, this group seems to be typical of the broader population. According to one website, there were 29.4 million searches made in the first year after the 2007 tax data [@citeAnderson]. @citenorway reported 920,896 unique users completed approximately more than 17 million searches. The mismatch may be attributed to the 2011 requirement that users check in to the official tax office website in order to search for tax data.

@@

The analysis will be conducted in R (@citeR), and the package we will use is tidyverse[@citetidyverse]. All graphs will be created using function ggplot2[@citeggplot2]. The packages knitr [@knitr] are also used to generate the R markdown report.

## Literature Review
Many researches have studies about the relationship between income transparency and happiness. Many suggested one's feeling of well-being is influenced by one's relative wealth. These findings contribute to the understanding of the Easterly Paradox, which states that an increase in wealth for everyone does not result in an increase in general happiness[@citePNAS]. Because utility is a matter of perspective, policymakers have been pushed to consider factors other than GDP. The so-called resource curse,' which refers to the propensity of resource-rich nations to underperform in a variety of social-economic outcomes, has piqued the public's attention in recent years. Recent research has gone beyond the usual influence on economic growth and instead examined the implications on wider indices of human well-being, such as infant mortality. In recent decades, a distinct empirical literature has investigated the factors of happiness and subjective well-being in more depth (using either country or household data).

In the paper "Happiness, Income, and Poverty," the author first presents some evidence that well-being is unquestionably related to income, but then explores two factors that imply GDP per capita may still play a role in happiness-based policy: subjective well-being inequality and the specific example of individuals who are in income poverty, both of which imply GDP per capita may still play a role in happiness-based policy[@citeClark]. Income inequality is a new component that is introduced in the study "The Effects of Income Levels and Income Inequalities on Happiness" by @citeTavor, which examines the relationship between happiness and income inequality. Happiness has been shown to have a negative impact at severe levels of inequality defined by the Gini index, independent of GDPppp per capita. This has been experimentally shown. On the other hand, across intermediate ranges of the Gini index, the relationship between index changes and pleasure is equivocal, as seen in Figure 1. These conclusions may be drawn independently of the actual figures of GDPppp per capita in the country. Bringing these two empirical lines of study together results in the publication "Happiness and the Resource Curse," by @citeAli, which is published in the Journal of Happiness Studies. This is the first research that we are aware of that takes use of a large panel dataset to investigate the relationships between changes in happiness across nations and different metrics of resource richness, according to the authors. Our findings, which are consistent with past empirical evidence of a resource curse in oil-rich countries, show that increases in oil rents are adversely related to increases in happiness over time. This 'resource curse' curse on happiness seems to be oil-specific, and it appears to hold true for both the levels and changes in levels of happiness.

@@

Subject Well-Being -- the main outcome of interest. The Norwegian Monitor Survey contains questions about happiness and life satisfaction, which are the two most extensively used measures of subjective well-being [citeEaster].

@@

Perceived Rank -- Based on the question: "Would you say that your economic condition is... in contrast to other Norwegians?" Slightly worse than average; Average; Slightly better than average; Much better than average." Using the Probit-OLS approach, these five categories were given values, and the variable was then standardized to have a mean of 0 and a standard deviation of 1. Greater values indicate a higher level of ranking.

@@

Linear regression

Dummy variable

Control variable

Coefficient

@@

```{r include=FALSE}
library(tidyverse)
library(haven)
library(tidyr)
library(reshape2)
```

```{r include=FALSE}
survey_data = read_dta("Raw-Norwegian-Monitor-Survey-Data.dta", encoding = 'latin1')
country_data = read_dta("google_searches_by_country.dta", encoding = 'latin1')
time_data = read_dta("google_searches_over_time.dta", encoding = 'latin1')
#names_data = read_dta("names_browsing_skattelister.dta", encoding = 'latin1')
```

@@

Perhaps the most compelling evidence comes from a Synovate poll done in 2007, which was representative of the whole taxable population of the United States at the time. Statistics on web traffic show that online tax listings are quite popular, which supports media reporting on their tremendous popularity in this area. According to one website, there were 29.4 million searches made in the first year after the publication of the 2007 tax data (which was published in January) [@citeAnderson]. On top of all of that, there is information that is publicly available from a time when tax records could only be accessed via the tax agency's official website. As reported by the @citenorway, 920,896 unique users completed slightly more than 17 million questions in the previous year, according to the most recent available data. 16 During that specific calendar year, only adults with a valid account were able to do searches on the official website. A total of 3,797,822 persons, or more than 24.25 percent of Norway's adult population, looked for at least one tax record in 2013, with the average user doing 18.46 searches. It is not feasible to directly compare figures from 2007 and 2013 since they are derived from a range of sources and are most likely based on different definitions, making direct comparison impossible. As a consequence of this restriction, the number of people doing searches, as well as the number of searches per capital, fell between 2007 and 2013. In most cases, this mismatch may be attributed to the 2011 requirement that users check in to the official tax office website in order to search for tax data, which was put in place in 2011.

@@

```{r echo=FALSE}
country_hah <- read.table(text = "keyword    Norway    Sweden
                  'Skattelister'   21.686750      0
                  'Tax'  7.228915      2.325581
                  'Weather'   18.072290      23.255819
                  'Youtube'   100.000000      100.000000
                  ",
                  header = TRUE, stringsAsFactors = FALSE)

df2 <- country_hah %>% 
  gather(Country, Value,-keyword)

countryaha <- ggplot(data = df2) +
  geom_bar(aes(x = keyword,
               y = Value,
               fill = Country
               ),
           stat = "identity",
           position = position_dodge()) +
  theme(legend.title=element_blank()) +
  labs(title ="Figure 1: Search Volumnes in Norway & Sweden (annually)", x = "Google search keyword", y = "Google searches relative to Youtube (%)")+theme_classic()
countryaha
```

When looking for tax documents on the internet, it's necessary to be familiar with the most often used words, as seen in Figure 1. By inserting the word "YouTube," we've provided a jumping-off point for other users. Norway has been located, which signifies that the quest has come to an end. A skattelister's test in Norway is no longer solely dependent on weather predictions as of the year 2010. A skattelister search accounted for almost one out of every five YouTube searches. This indicates that there is a great deal of interest in the tax listings. Norwegians were found to be more prone than the overall population to look for tax paperwork, according to the study. While it is true that people have an increased interest in taxation, tax lists were searched approximately three times more often than actual taxes.

```{r}
time_date3 = melt(time_data, id.vars = "edate", measure.vars = c("tax", "weather","skattelister","youtube"))

time_date3%>%
  rename(Keyword = variable)%>%
  ggplot(aes(x=edate, y=value, group=Keyword, color=Keyword))+geom_line()+theme_classic()+labs(title  = "Figure 2: Search Volumes in Norway (bi- weekly)", x = "Time interval (every 2 weeks)", y = "Google search Volumes")+theme(axis.text.x = element_text(angle = 90, size = 8))+scale_x_date(date_labels="%b %y",date_breaks  ="2 week")
```

@@

```{r include=FALSE}
# Descriptive statistics for the main variables from the noeweigian ...
data1 <- survey_data  %>% filter(!is.na(happy)) %>% summarise(sd(happy), mean(happy)) 
data1
```

@@

The coefficient $\alpha_1$ represents the average change of happiness level (between the year 1985 and 2000) with one unit change of $\IncomeRank_i,_t$, holding other variables constant. Based on our assumption, if the value of this coefficient is positive, we can say that there might be a positive relationship between income level and happiness level. Practically, the subject well-being of an individual at certain year is associated with "being richer" as per the gain from purchases of better goods and services and the gain from "income comparison", one became more confident with higher income. Similarly, $\alpha_2$ represents the additional happiness from the changing happiness-income gradient from 2001 to 2013 (as the dummy variable become 1 in this time frame. 0 when the period from 1985 to 2000). The positive value indicates that the higher transparency raises the gradient of happiness-income.

```{r}
survey_data1 = survey_data %>%
  mutate(transparency = if_else(year %in% 2001:2013, 1,0))
model0=lm(happy~inc_comparison+inc_comparison:transparency,data=survey_data1)
summary(model0)
```

@@

@@

# Conclusions

>>>>

---
title: "Happiness versus Income Awareness"
subtitle: "Will people be happier if they know each other's income?"
author: 
  - Xiao Bai
  - Yichun Zhang
date: "27/02/2022"
output:
  pdf_document:
    toc: true
    toc_depth: 2
abstract: "In 2001, tax records in Norwey becaome easily accessible online, which allows everyone to see their income level and make comparsion with other people's income. The populatiry of searching the word 'Skattelister' (tax record list) has increased significantly since the introduction of tax data in 2001. People has large interest in the tax lists: for every five searches for YouTube, there was about one for skattelister. However, the introduction of this tax record list would cause a negative effect on the public as the income comparision model reports that the visible income transparency can exntend the disparity in well-being between groups of people with higher and lower income. "
bibliography: references.bib
---

@@

Based on information gathered by the Norwegian Monitor Survey, an annual self-completion questionnaire was disseminated to an ethnically diverse sample of Norwegians between 1985 and 2013. In terms of several apparent qualities, this group seems to be typical of the broader population. According to one website, there were 29.4 million searches made in the first year after the 2007 tax data [@citeAnderson]. Norway Ministry of Finance (2014) reported 920,896 unique users completed approximately more than 17 million searches. The mismatch may be attributed to the 2011 requirement that users check in to the official tax office website in order to search for tax data.

@@

The analysis will be conducted in R [@citeR], and the package we will use is tidyverse [@citetidyverse]. All graphs will be created using function ggplot2 [@citeggplot2]. The packages knitr [@citeknitr] are also used to generate the R markdown report.

## Literature Review
Many researches have studies about the relationship between income transparency and happiness. Many suggested one's feeling of well-being is influenced by one's relative wealth. These findings contribute to the understanding of the Easterly Paradox, which states that an increase in wealth for everyone does not result in an increase in general happiness [@citePNAS]. Because utility is a matter of perspective, policymakers have been pushed to consider factors other than GDP. The so-called resource curse,' which refers to the propensity of resource-rich nations to underperform in a variety of social-economic outcomes, has piqued the public's attention in recent years. Recent research has gone beyond the usual influence on economic growth and instead examined the implications on wider indices of human well-being, such as infant mortality. In recent decades, a distinct empirical literature has investigated the factors of happiness and subjective well-being in more depth (using either country or household data).

In the paper "Happiness, Income, and Poverty," the author first presents some evidence that well-being is unquestionably related to income, but then explores two factors that imply GDP per capita may still play a role in happiness-based policy: subjective well-being inequality and the specific example of individuals who are in income poverty, both of which imply GDP per capita may still play a role in happiness-based policy [@citeClark]. Income inequality is a new component that is introduced in the study "The Effects of Income Levels and Income Inequalities on Happiness" by @citeTavor, which examines the relationship between happiness and income inequality. Happiness has been shown to have a negative impact at severe levels of inequality defined by the Gini index, independent of GDPppp per capita. This has been experimentally shown. On the other hand, across intermediate ranges of the Gini index, the relationship between index changes and pleasure is equivocal, as seen in Figure 1. These conclusions may be drawn independently of the actual figures of GDPppp per capita in the country. Bringing these two empirical lines of study together results in the publication "Happiness and the Resource Curse," by @citeAli, which is published in the Journal of Happiness Studies. This is the first research that we are aware of that takes use of a large panel dataset to investigate the relationships between changes in happiness across nations and different metrics of resource richness, according to the authors. Our findings, which are consistent with past empirical evidence of a resource curse in oil-rich countries, show that increases in oil rents are adversely related to increases in happiness over time. This 'resource curse' curse on happiness seems to be oil-specific, and it appears to hold true for both the levels and changes in levels of happiness.

@@

Subject Well-Being -- the main outcome of interest. The Norwegian Monitor Survey contains questions about happiness and life satisfaction, which are the two most extensively used measures of subjective well-being [@citeEaster].

@@

Perceived Rank -- Based on the question: "Would you say that your economic condition is... in contrast to other Norwegians?" Slightly worse than average; Average; Slightly better than average; Much better than average.

@@

Linear regression: Linear regression is primarily used as the analysis model in the original paper and the reproduction paper, to analyze the association between individual well-being, income rank, and the impact of income transparency.

Dummy variable: Dummy variable was introduced in the OLS regression to account for the impact of the presence of income transparency. If the time period of data exists between 2001-2013 the dummy variable became 1 to account for such effect and vice versa.

Coefficient: Coefficient for the OLS regression represents the slope for income rank, indicating the degree of impact of income rank on one's well-being. It is mainly used in the original paper to compare the impact on individual well-being regarding presence of income transparency.

@@

```{r, message = FALSE, include = FALSE}
#Read the packages and use these packages to complete following analysis
library(tidyverse)
library(haven)
library(tidyr)
library(reshape2)
```

```{r, echo=FALSE}
#Since our data are dta format, we need to import all data first and then open these data using read_dta function. These data are saved in a new dataframe with their corresponding names.

survey_data = read_dta("Raw-Norwegian-Monitor-Survey-Data.dta", encoding = 'latin1')
country_data = read_dta("google_searches_by_country.dta", encoding = 'latin1')
time_data = read_dta("google_searches_over_time.dta", encoding = 'latin1')

```

@@

Perhaps the most compelling evidence comes from a Synovate poll done in 2007, which was representative of the whole taxable population of the United States at the time. Statistics on web traffic show that online tax listings are quite popular, which supports media reporting on their tremendous popularity in this area. According to one website, there were 29.4 million searches made in the first year after the publication of the 2007 tax data (which was published in January) [@citeAnderson]. On top of all of that, there is information that is publicly available from a time when tax records could only be accessed via the tax agency's official website. As reported by the Norway Ministry of Finance (2014), 920,896 unique users completed slightly more than 17 million questions in the previous year, according to the most recent available data. 16 During that specific calendar year, only adults with a valid account were able to do searches on the official website. A total of 3,797,822 persons, or more than 24.25 percent of Norway's adult population, looked for at least one tax record in 2013, with the average user doing 18.46 searches. It is not feasible to directly compare figures from 2007 and 2013 since they are derived from a range of sources and are most likely based on different definitions, making direct comparison impossible. As a consequence of this restriction, the number of people doing searches, as well as the number of searches per capital, fell between 2007 and 2013. In most cases, this mismatch may be attributed to the 2011 requirement that users check in to the official tax office website in order to search for tax data, which was put in place in 2011.

@@

When looking for tax documents on the internet, it's necessary to be familiar with the most often used words, as seen in Figure 1. By inserting the word "YouTube," we've provided a jumping-off point for other users. Norway has been located, which signifies that the quest has come to an end. A skattelister's test in Norway is no longer solely dependent on weather predictions as of the year 2010. A skattelister search accounted for almost one out of every five YouTube searches. This indicates that there is a great deal of interest in the tax listings. Norwegians were found to be more prone than the overall population to look for tax paperwork, according to the study. While it is true that people have an increased interest in taxation, tax lists were searched approximately three times more often than actual taxes.
```{r echo=FALSE}
#Since the original data contain many observations that exceed the maximum load and are useless for further analysis, we create a new table with the corresponding variables and then plot a bar graph.
country_hah <- read.table(text = "keyword    Norway    Sweden
                  'Skattelister'   21.686750      0
                  'Tax'  7.228915      2.325581
                  'Weather'   18.072290      23.255819
                  'Youtube'   100.000000      100.000000
                  ",
                  header = TRUE, stringsAsFactors = FALSE)

#We try to let R read the variables, so we use gather function
df2 <- country_hah %>% 
  gather(Country, Value,-keyword)
#Plot a bar graph using ggplot, with appropriate x and y labels and title. Different color represents different countries, so we use fill to specify that. Because classic theme is easier to read, so we also use that.
countryaha <- ggplot(data = df2) +
  geom_bar(aes(x = keyword,
               y = Value,
               fill = Country
               ),
           stat = "identity",
           position = position_dodge()) +
  theme(legend.title=element_blank()) +
  labs(title ="Figure 1: Search Volumes in Norway & Sweden (annually)", x = "Google search keyword", y = "Google searches relative to Youtube (%)")+theme_classic()
countryaha
```

@@

```{r, echo=FALSE}
#Since the author use Stata to conduct analysis, the format of data is quite different than conducting using R, so we use melt function to takes data in wide format and stacks a set of columns into a single column of data, and save it into time_data3
time_date3 = melt(time_data, id.vars = "edate", measure.vars = c("tax", "weather","skattelister","youtube"))

#We plot a line graph to show how the volumes of searches change by time in Norway. We set the tick labels to size 8 and angle 90 to make it more readable.
time_date3%>%
  rename(Keyword = variable)%>%
  ggplot(aes(x=edate, y=value, group=Keyword, color=Keyword))+geom_line()+theme_classic()+labs(title  = "Figure 2: Search Volumes in Norway (bi-weekly)", x = "Time interval (every 2 weeks)", y = "Google search Volumes")+theme(axis.text.x = element_text(angle = 90, size = 8))+scale_x_date(date_labels="%b %y",date_breaks  ="2 week")
```

@@

The coefficient $\alpha_1$ represents the average change of happiness level (between the year 1985 and 2000) with one unit change of income rank, holding other variables constant. Based on our assumption, if the value of this coefficient is positive, we can say that there might be a positive relationship between income level and happiness level. Practically, the subject well-being of an individual at certain year is associated with "being richer" as per the gain from purchases of better goods and services and the gain from "income comparison", one became more confident with higher income. Similarly, $\alpha_2$ represents the additional happiness from the changing happiness-income gradient from 2001 to 2013 (as the dummy variable become 1 in this time frame. 0 when the period from 1985 to 2000). The positive value indicates that the higher transparency raises the gradient of happiness-income.

```{r, include = FALSE}
#This section we conduct a regression model using lm function and OLS regression. We first mutate a new variable called transparency to separate the time interval, and then make a model using happy as dependent variable and income rank as independent variable. Then we use summary function to display results in a table form.
survey_data1 = survey_data %>%
  mutate(transparency = if_else(year %in% 2001:2013, 1,0))
model0=lm(happy~inc_comparison+inc_comparison:transparency,data=survey_data1)
summary(model0)
```

@@

Table: Results of Regression Model

@@

# Conclusion
